Road traffic sound level estimation from realistic urban sound mixtures by Non-negative Matrix Factorization

### 2018-03-06 paper/gloaguenAppliedNMF.tex
removed unnecessary figures + add reference in biblio

An other approach, followed in this paper, is to consider the Blind Source Separation paradigm, see Figure \ref{fig:source_separation}, which consists in the extraction of a specific signal inside a set of mixed signals. From the different existing methods (CASA, ICA), Non-negative Matrix Factorization (NMF) \cite{lee_learning_1999}, seems the most relevant method for monophonic sensor networks. Dealing easily with the overlapping between the sound sources, this method approximes the magnitude spectrogram of a single signal by the product of two non negative matrices. A lot of applications can be found for musical \cite{smaragdis_non-negative_2003, benetos2006musical} and speech \cite{wilson_speech_2008, mysore2011non} contents. Dedicated to sound separation, Immani and Kasa\"i \cite{satoshi_innami_nmf-based_2012} used NMF in a two steps sound separation with the help of time variant gain features. A first study [article JASM] has been conducted, in which diverse NMF formula, namely the supervised, the semi-supervised, and the threshold initialized NMF, have been applied on a large set of simulated sound scenes that which mixed traffic component with specific urban sounds at calibrated sound levels. The study proved the interest of NMF for urban sound environments and compared the benefits of each approach. However, it has now to face to real urban sound scenes.

@@

The allure of $D_{\theta}\left(\mathbf{W_0} \Vert \mathbf{W'} \right)$ and $\alpha$ are displayed in Figure \ref{fig:example_threshold}.\\

\begin{figure}[t]
    \centering
       \includegraphics[width=0.9\linewidth]{./figures/thresh.pdf}
    \caption{Evolution of the $\alpha$ weight according to $D_{\theta}\left(\mathbf{W_0} \Vert \mathbf{W'} \right)$ for hard thresholding with $t_h$ = 0.6 (in dashed line)}
    \label{fig:example_threshold}
\end{figure}

>>>>

An other approach, followed in this paper, is to consider the Blind Source Separation paradigm, see Figure \ref{fig:source_separation}, which consists in the extraction of a specific signal inside a set of mixed signals. From the different existing methods (CASA, ICA), Non-negative Matrix Factorization (NMF) \cite{lee_learning_1999}, seems the most relevant method for monophonic sensor networks. Dealing easily with the overlapping between the sound sources, this method approximes the magnitude spectrogram of a single signal by the product of two non negative matrices. A lot of applications can be found for musical \cite{smaragdis_non-negative_2003, benetos2006musical} and speech \cite{wilson_speech_2008, mysore2011non} contents. Dedicated to sound separation, Immani and Kasa\"i \cite{satoshi_innami_nmf-based_2012} used NMF in a two steps sound separation with the help of time variant gain features. A first study \cite{gloaguen2018Estimation} has been conducted, in which diverse NMF formula, namely the supervised, the semi-supervised, and the threshold initialized NMF, have been applied on a large set of simulated sound scenes that which mixed traffic component with specific urban sounds at calibrated sound levels. The study proved the interest of NMF for urban sound environments and compared the benefits of each approach. However, it has now to face to real urban sound scenes.

@@
